APPM report - Draft

### 2022-10-21 paper_version/main.tex
Polish spatial semi-discretization

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{subcaption}
\usepackage{authblk}

@@

The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses challenge for simulations over different regimes. Such phenomena occur in many problems, e.g. vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}. Asymptotic-preserving schemes are the ones that perform uniformly well in such asymptotic limit. To briefly illustrate the concept, see the commutative diagram Fig. \ref{fig:commutative_diagram_ap} in \cite{jin_1999}. The parametrized problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, is discretized by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g. mesh size. The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. In the other word, an AP scheme $P^\lambda_h$ makes the diagram Fig. \ref{fig:commutative_diagram_ap} commutative. For more details about AP schemes, see \cite{jin_2010, degond_2017} for comprehensive reviews.

@@

The content of this paper is organized as follows. In Section 2, we first give full details on the underlying equations of the Maxwell-Euler system and its rescaling procedure. Afterwards we introduce the ECE-type boundary conditions for our problem. A reformulation of the Maxwell equations in the insulating region is then presented. Section 3 is devoted to the discretization. \todo{outline}

@@

\section{Plasma model}
\begin{comment}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations. The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.

@@

The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system. The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for the Maxwell equations. The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD. The advantage of the FVM-FIT framework lie in the \emph{discrete exterior calculus} (DEC) nature of FIT and straightforward coupling of both systems through the primal-dual mesh pair. These would be made clear in the corresponding sections.

@@

\subsection{The Maxwell-Euler System}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations. The Maxwell equations take charge of their interaction with electromagnetic fields. For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.

The Maxwell's equations in SI units read
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media in vacuum. We consider the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

@@

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems is due to the following relations that connect the fluid and electromagnetic quantities
\begin{equation*}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation*}

@@

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametrized system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
\end{subequations}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons takes the expression
\begin{align*} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align*}

@@

\subsection{Quasi-neutral limit} \label{sec:quasi-neutral_limit}
The Debye length $\lambda_D$ (see its definition at the preceding section) is an characteristic length over which local concentrations of charge are shielded out. For the underlying physics, see \cite[Sec. 1.4]{chen2016}. In many situations, it has a rather low value compared to the interested length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch. 20]{Blandford_2013}. That justifies the quasi-neutrality assumption that the plasma is locally neutral, namely $\rho = \sum_* q_*n_* = 0$. The limit model is obtained by formally taking the rescaled Debye length $\lambda$ to zero:
\vspace{-\baselineskip}
\begin{center}
    \begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0,\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0, \\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho.
\end{align*}
\end{subequations}

@@

\subsection{Boundary conditions}

@@

\begin{remark}
    The treatment of electrodes as open boundary is a rather simplified approach. \todo{a realistic BC for electrodes.}
\end{remark}

The Maxwell system is defined on the whole domain $\Omega$. External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes. More specifically, $\Gamma_C$ is usually composed of disjoint connecting components $\Gamma_C^i$, $i \leq N$ where $N$ is total number of these boundary components. Constant potentials are enforced on each component in the sense that $\varphi|_{\Gamma_C^i} = \varphi_i$. The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector. \todo{A few works on ECE BC?} 
\begin{figure}
\begin{minipage}{0.45\textwidth}
    \resizebox{\textwidth}{!}{
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}}
\end{minipage}
\begin{minipage}{0.49\textwidth}
    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[violet] (A2) -- node[above]{\color{gray}Insulating domain $\Omega_I$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
        \draw[violet] (A3) -- node[below]{\color{gray}Insulating domain $\Omega_I$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^1$} (A3);
        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
        \node at (3,0) {Plasma domain $\Omega_P$};
        \begin{scope}[shift={(6.5,-1.6)}]
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
        \end{scope}
    \end{tikzpicture}}
\end{minipage}
\caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
\label{fig:domain_sketch}
\end{figure}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Maxwell equations:}
    \begin{align*}
    \varphi &= \varphi^i(t)\ \ \text{on} \ \ \Gamma_C^i, \\
    \text{curl} \mathbf{E} \cdot \mathbf{n} &= 0\ \ \text{on} \ \  \Gamma_I,  \\
    \text{curl} \mathbf{H} \cdot \mathbf{n} &= 0\ \  \text{on} \ \  \Gamma_I.\
    \end{align*}
\end{minipage}

@@

\begin{remark}
    A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^i$. Since the surface curl $\text{curl}_\gamma\mathbf{E} = \text{curl} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator. However, for a geometric setting with non-trivial geometry, one needs to consider co-homology vector fields\cite{Hiptmair_2021}.
\end{remark}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\usepackage{authblk}

@@

The quasi-neutral limit of the Maxwell system leads to a singularly perturbed problem in the sense that the system changes its type from hyperbolic to a mixture of hyperbolic, parabolic and elliptic, which poses challenge for simulations over different regimes. Such phenomena occur in many physical models, e.g. vanishing viscosity in the Navier-Stokes equations\cite{Kato_1984}, zero-relaxation-limit of kinetic equations\cite{jin_2010} and zero-Mach-limit of compressible flows\cite{degond_2007, haack_2010}. It is desirable that numerical schemes are valid for all ranges of scaled parameters, and especially when they goes to zero. These schemes are said to be \emph{asymptotic-preserving}. The concept is sketched by the commutative diagram Fig. \ref{fig:commutative_diagram_ap} in \cite{jin_1999}. The parametric problem $P^\lambda$, which converges to its limit $P^0$ as the perturbed parameter $\lambda \rightarrow 0$, is discretized by the scheme $P^\lambda_h$ where $h$ denotes some discretization parameter, e.g. mesh size. The AP property requires the uniform convergence of $P^\lambda_h$ to the $P^\lambda$ as $\lambda\rightarrow0$. In the other word, an AP scheme $P^\lambda_h$ makes the diagram Fig. \ref{fig:commutative_diagram_ap} commutative. For more details about AP schemes, see \cite{jin_2010, degond_2017} for comprehensive reviews.

@@

The content of this paper is organized as follows. In Section 2, we first give full details on the underlying equations of the Maxwell-Euler system and its rescaling procedure. Afterwards we introduce the ECE-type boundary conditions for our problem. A reformulation of Maxwell's equations in the insulating region is then presented. Section 3 is devoted to the discretization. \todo{outline}

@@

\section{Plasma model}
\begin{comment}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations. Maxwell's equations are involved to describe their induction of and interaction with electromagnetic fields.

@@

The other emphasis of this work is the development of a 3D discretization framework for the Maxwell-Euler system. The key ingredient is the combination of the Finite Volume Method (FVM) for the Euler equations and the Finite Integration Technique (FIT) for Maxwell's equations. The latter one is usually treated as a generalization to Yee's scheme \citep{yee_1966} or FDTD. The advantage of the FVM-FIT framework lie in the \emph{discrete exterior calculus} (DEC) nature of FIT and straightforward coupling of both systems through the primal-dual mesh pair. These would be made clear in the corresponding sections.

@@

\subsection{The Maxwell-Euler System}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations. Maxwell's equations take charge of their interaction with electromagnetic fields. For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.

The Maxwell's equations in SI units read
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media in vacuum. We consider the linear constitutive relations 
\begin{equation} \label{equ:material_law}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

@@

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems is due to the following relations that connect the fluid and electromagnetic quantities
\begin{equation} \label{equ:maxwell_euler_coupling}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation}

@@

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametric system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
\end{subequations}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons takes the expression
\begin{align*} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align*}

@@

\subsection{Quasi-neutral Limit} \label{sec:quasi-neutral_limit}
The Debye length $\lambda_D$ (see its definition at the preceding section) is an characteristic length over which local concentrations of charge are shielded out. For the underlying physics, see \cite[Sec. 1.4]{chen2016}. In many situations, it has a rather low value compared to the interested length scale: the typical $\lambda_D$ for gas discharge and Tokamak is $10^{-4}$ m; for interstellar medium, the magnitude is about $1$ m \cite[ch. 20]{Blandford_2013}. That justifies the quasi-neutrality assumption that the plasma is locally neutral, namely $\rho = \sum_* q_*n_* = 0$. The limit model is obtained by formally taking the rescaled Debye length $\lambda$ to zero:
\vspace{-\baselineskip}
\begin{center}
    \begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0,\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0, \\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho.
\end{align*}
\end{subequations}

@@

\subsection{Boundary Conditions} \label{sec:BC}

@@

\begin{remark}
    The treatment of electrodes as open boundary is a rather simplified approach. For more realistic electrode modelling, see \cite{godyak_1990, parker_1993}.
\end{remark}

The Maxwell system is defined on the whole domain $\Omega$. External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes. More specifically, $\Gamma_C$ is composed of two disjoint connecting components $\Gamma_C^\pm$. Constant potentials are enforced on each component in the sense that $\Phi|_{\Gamma_C^\pm} = \Phi_\pm$. The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector. \todo{A few works on ECE BC?} 
\begin{figure}
\begin{minipage}{0.45\textwidth}
    \resizebox{\textwidth}{!}{
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}}
\end{minipage}
\begin{minipage}{0.49\textwidth}
    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[violet] (A2) -- node[above]{\color{gray}Insulating domain $\Omega_I$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
        \draw[violet] (A3) -- node[below]{\color{gray}Insulating domain $\Omega_I$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^1$} (A3);
        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
        \node at (3,0) {Plasma domain $\Omega_P$};
        \begin{scope}[shift={(6.5,-1.6)}]
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
        \end{scope}
    \end{tikzpicture}}
\end{minipage}
\caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
\label{fig:domain_sketch}
\end{figure}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For Maxwell's equations:}
    \begin{align*}
    \Phi = \Phi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm, \\
    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I.\
    \end{align*}
\end{minipage}

@@

\begin{remark}
    A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^\pm$. Since the surface curl $\text{\emph{curl}}_\gamma\mathbf{E} = \text{\emph{curl}} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator. However, for a geometric setting with non-trivial geometry, one needs to consider co-homology vector fields \cite{Hiptmair_2021}.
\end{remark}

\subsection{Reformulation} \label{sec:reform_continuous}
In the insulating domain $\Omega_I$ (see Fig. \ref{fig:sketch_domain}), the Euler system is not defined there due to the absence of plasmas. Consequently, the Maxwell system in $\Omega_I$ is described by
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}
